### 2021-02-24 yfcc100m/paper/vldb2021/eval.tex
Update intro and design, minor changes in eval
Update intro/eval design, add more references
changed plot to only build sizes

\begin{figure}[ht]
\centering
\includegraphics[width=\columnwidth]{figures/all_build_times_plot}
\caption{Time to build and size (in GB) of MySQL, PostgreSQL, and VDMS databases.}
\label{fig:db_time_size}
\end{figure}

\subsubsection{Database Building Time}

One of the first things we noticed is the difference in the time needed to
build each database, where VDMS outperforms MySQL by a large margin
but PostgreSQL outperforms VDMS by a large margin as well.
This analysis includes only the metadata, as the images are stored
in a shared filesystem. Figure~\ref{fig:db_time_size} illustrates the
comparison in time to build the databases, and how the speedup
is sustained as the database size grows.
Key difference in the build times are attributed to the low-level
implementation of how MySQL reads and stores data from the files, the
optimizations (increased InnoDB pool size, etc.) needed
to handle large datasets such as YFCC100M, and the efficiency of PMGD.
PostgreSQL Python API can efficiently copy data from files to the database
which provides an advantage over VDMS which must insert multiple nodes/connections per image.
On average, it took MySQL around $\sim$4x longer to build each database than VDMS,
and PostgreSQL was around $\sim$21x faster than VDMS.

@@

Another important aspect to note is the storage footprint of the databases.
PostgreSQL and VDMS require comparable amount of storage for metadata which
is more than required by MySQL, shown in Figure~\ref{fig:db_time_size}.
In the case of VDMS, this is space used to store information about
each node/connection.
The Graph Database internal to VDMS (called PMGD) was designed for performance,
especially in environments where persistent memory is present.
This design decision comes as a trade-off for storage footprint, which is
noticeable in our results.
VDMS required 37-41\% more storage than MySQL for storing the same amount
of metadata. On the other hand, PostgreSQL required 1-4\% more storage than VDMS.
The storage footprint may become a factor if storage is a limitation, but
it should also be noted that metadata accounts for less than 2\% of the
overall database size even if we have a 41\% increase in metadata size.
For example, the largest database (both metadata and images) we built
(100M) has around 230GB of metadata and 12TB of images.
In systems where persistent memory is a scarce resource,
the increased storage foot print of PMGD may represent a challenge.
On the other hand, persistent memory is expected to be available
in the order of TBs per server, which should fit the
metadata of intensive use-cases\cite{IntelXPoint15}.

@@

\begin{figure}[ht]
% WAS: begin{figure*}[ht]; textwidth
\includegraphics[width=\columnwidth]{figures/plot_conc_q_1tag_loc20_resize_mosaic_results_throughput_db_size}
\caption{Concurrency Analysis on \textit{q2} (\textit{1tag\_geo\_resize}) from our use-case
described in the Experimental Setup Section.
We show each database in different figures for readability reasons.
The figures show the throughput (images per second) when retrieving
resized versions of the images, as the number of concurrent clients increases
Hardware concurrency (number of physical cores in each system)
is shown with a blue vertical line (hw-concurrency = 56).}
\label{fig:concurrency_comparison_q2}
\end{figure}

>>>>

% \begin{figure}[ht]
% \centering
% \includegraphics[width=\columnwidth]{figures/all_build_times_plot}
% \caption{Time to build and size (in GB) of MySQL, PostgreSQL, and VDMS databases.}
% \label{fig:db_time_size}
% \end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=\columnwidth]{figures/all_build_sizes_plot}
\caption{Data footprint (in GB) of MySQL, PostgreSQL, and VDMS databases.}
\label{fig:db_sizes}
\end{figure}

% \subsubsection{Database Building Time}

% One of the first things we noticed is the difference in the time needed to
% build each database, where VDMS outperforms MySQL by a large margin
% but PostgreSQL outperforms VDMS by a large margin as well.
% This analysis includes only the metadata, as the images are stored
% in a shared filesystem. Figure~\ref{fig:db_time_size} illustrates the
% comparison in time to build the databases, and how the speedup
% is sustained as the database size grows.
% Key difference in the build times are attributed to the low-level
% implementation of how MySQL reads and stores data from the files, the
% optimizations (increased InnoDB pool size, etc.) needed
% to handle large datasets such as YFCC100M, and the efficiency of PMGD.
% PostgreSQL Python API can efficiently copy data from files to the database
% which provides an advantage over VDMS which must insert
% multiple nodes/connections per image.
% On average, it took MySQL around $\sim$4x longer to build each database than VDMS,
% and PostgreSQL was around $\sim$21x faster than VDMS.

@@

% Another important aspect to note is the storage footprint of the databases.
PostgreSQL and VDMS require comparable amount of storage for metadata which
is more than required by MySQL, shown in Figure~\ref{fig:db_sizes}.
In the case of VDMS, this is space used to store information about
each node/connection.
The Graph Database internal to VDMS (called PMGD) was designed for performance,
especially in environments where persistent memory is present.
This design decision comes as a trade-off for storage footprint, which is
noticeable in our results.
VDMS required 37-41\% more storage than MySQL for storing the same amount
of metadata. On the other hand, PostgreSQL required 1-4\% more storage than VDMS.
The storage footprint may become a factor if storage is a limitation, but
it should also be noted that metadata accounts for less than 2\% of the
overall database size even if we have a 41\% increase in metadata size.
For example, the largest database (both metadata and images) we built
(100M) has around 230GB of metadata and 12TB of images.
In systems where persistent memory is a scarce resource,
the increased storage foot print of PMGD may represent a challenge.
On the other hand, persistent memory is expected to be available
in the order of TBs per server, which should fit the
metadata of intensive use-cases\cite{IntelXPoint15}.

@@

\begin{figure}[ht]
% WAS: begin{figure*}[ht]; textwidth
\includegraphics[width=\columnwidth]{figures/plot_conc_q_1tag_geo_resize_mosaic_results_throughput_db_size}
\caption{Concurrency Analysis on \textit{q2} (\textit{1tag\_geo\_resize}) from our use-case
described in the Experimental Setup Section.
We show each database in different figures for readability reasons.
The figures show the throughput (images per second) when retrieving
resized versions of the images, as the number of concurrent clients increases
Hardware concurrency (number of physical cores in each system)
is shown with a blue vertical line (hw-concurrency = 56).}
\label{fig:concurrency_comparison_q2}
\end{figure}
